Computing astrophysical inferences with diffusive nested sampling

### 2014-02-23 ms.tex
Simulated tempering
Fixed url

\author{Brendon J. Brewer}{
  address={Department of Statistics, The University of Auckland\\
http://stat.auckland.ac.nz/\~{ }brewer/}
}

@@

The zeroth component of this mixture is just the prior $p(\pars)$. The first
mixture component is the prior, but restricted to the domain where the
likelihood is greater than a threshold $L^*_1$. The second mixture component
is the prior, but restricted to the domain where the likelihood is above
$L^*_2$. The likelihood thresholds $\{ L^*_i \}$ are chosen so each
successive constrained prior occupies approximately $\exp(-1)$ times as much
prior mass (``volume'') as the previous constrained prior.

>>>>

\author{Brendon J. Brewer}{
  address={Department of Statistics, The University of Auckland\\
http://www.stat.auckland.ac.nz/\~{ }brewer/}
}

@@

The zeroth component of this mixture is just the prior $p(\pars)$. The first
mixture component is the prior, but restricted to the domain where the
likelihood is greater than a threshold $L^*_1$. The second mixture component
is the prior, but restricted to the domain where the likelihood is above
$L^*_2$. The likelihood thresholds $\{ L^*_i \}$ are chosen so each
successive constrained prior occupies approximately $\exp(-1)$ times as much
prior mass (``volume'') as the previous constrained prior. This is strongly
related to the algorithm known as ``simulated tempering''
\citep{simulated_tempering}, but uses NS's
sequence of intermediate distributions instead of an annealed sequence.
